Economic Evaluation of Geographically Weighted Regression Analysis for Site-specific Nitrogen Management

### 2022-09-07 Writing/manuscript_gwr.rmd
manuscript updates according to the comments

```{r figure_setup, cache = F}
theme_update(
  axis.title.x =
    element_text(
      size = 12, angle = 0, hjust = .5, vjust = -0.3, face = "plain"
    ),
  axis.title.y =
    element_text(
      size = 12, angle = 90, hjust = .5, vjust = .9, face = "plain"
    ),
  axis.text.x =
    element_text(
      size = 10, angle = 0, hjust = .5, vjust = 1.5, face = "plain"
    ),
  axis.text.y =
    element_text(
      size = 10, angle = 0, hjust = 1, vjust = 0, face = "plain"
    ),
  axis.ticks =
    element_line(
      size = 0.3, linetype = "solid"
    ),
  axis.ticks.length = unit(.15, "cm"),
  #--- legend ---#
  legend.text =
    element_text(
      size = 10, angle = 0, hjust = 0, vjust = 0, face = "plain"
    ),
  legend.title =
    element_text(
      size = 10, angle = 0, hjust = 0, vjust = 0, face = "plain"
    ),
  legend.key.size = unit(0.5, "cm"),
  #--- strip (for faceting) ---#
  strip.text = element_text(size = 10),
  #--- plot title ---#
  plot.title = element_text(family = "Times", face = "bold", size = 12),
  #--- margin ---#
  # plot.margin = margin(0, 0, 0, 0, "cm"),
  #--- panel ---#
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background = element_blank(),
  panel.border = element_rect(fill = NA)
)
```

@@

**Abstract**: Geographically weighted regression (GWR) has been presented as a prominent tool to estimate site-specific yield response functions to generate site-specific input rate recommendations using data generated by on-farm precision experimentation (OFPE). The key objectives of this paper are two-fold. First, it evaluates two sets of functional-form specifications used by two recent published studies of site-specific input management that apply GWR to data from OFPE. We show that one set of functional-form specification performs significantly better than the other under three price scenarios observed historically. Second, we investigate the possibility of bias in estimating the "economic" value of site-specific recommendation maps based on GWR. We show that GWR suffers significant positive bias, which can lead to great over-estimation of the "economic" value of applying GWR methods. Our study is the first to systematically examine the "economic" properties of the use of GWR in OPFE settings. We reveal that in many circumstances using GWR is far less profitable than claimed by previous studies, which provides a necessary cautionary message to researchers who might otherwise “over-sell” to other researchers the value of using GWR methods in empirical work involving the estimation of site-specific input management.

@@

In recent years, On-farm Precision Experimentation (OFPE) has gained traction with both researchers and practitioners as a means of generating high-resolution spatial data to inform site-specific crop input management decisions [@bullock2019data; @lacoste2021farm]. Accompanying interest is surging among researchers in identifying efficient statistical methods to estimate site-specific yield response functions, which have examined various methods, ranging from Geographically Weighted Regression (GWR) [@rakshit2020; @evans2020assessment; @trevisan2021spatial] to machine learning methods including random forest [@krause2020random] and convolutional neural network [@barbosa2020modeling] approaches. Among these methods applied to OFPE data, GWR is distinct in that it does not require potentially costly collection of site-specific field and soil information in estimating site-specific yield response functions.

@@

However, deploying sophisticated sensors to gather field characteristics data is also costly, and the effects of their generation and use on farming profitability remains in question [@gardner2021economic]. Recognizing the significant costs of obtaining useful, high-resolution soil and field properties data, @trevisan2021spatial demonstrated a method of providing site specific management recommendations without such data. The study estimated site-specific yield response functions by applying GWR techniques on data from OFPEs [@bullock2019data]. @trevisan2021spatial reported dramatic results, estimating an average potential gain of \$65 ha$^{-1}$ from applying seed and N at optimal uniform rates (instead of at the rates the farmers would have chosen if not participating in the research), and an additional potential gain of \$58 ha$^{-1}$ when changing from optimal uniform application rates to optimal site-specific application rates. This is rather surprising give the poor accuracy of GWR estimates [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation]. @rakshit2020 also applied GWR to on-farm experiment data. However, while they did estimate site-specific yield response functions, they did not derive site-specific economically optimal nitrogen rates based on them, and thus did not conduct economic analysis unlike @trevisan2021spatial. @evans2020assessment explored using GWR with a linear model specification to detect low- and high-response areas, but like @rakshit2020, they also did not estimate site-specific economically optimal nitrogen rates.

@@

Second, we will examine the degree and direction of bias in the estimation of the "economic" value of GWR-based variable rate application (VRA) and question the extremely high estimates of that value reported by @trevisan2021spatial (It is critical to keep in mind that it is not our objective at all to see the bias in the coefficient estimation by GWR, unlike [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation]. Rather, we are interested in its economic implication in this study.). In general, researchers take the following steps to estimate the value of VRA based using OFPE data [e.g., @anselin2004spatial; @swinton1998evaluating; @bullock2002adding;  @liu2006site]: (1) estimate site-specific yield response functions based on a method chosen by the researcher; (2) use the estimated yield response functions to estimate the economically optimal site-specific input rates (EOIR) and economically optimal uniform input rates; (3) plug the estimated site-specific EOIRs and uniform EOIR into the estimated yield response functions to calculate estimated profits under both strategies; and (4) find the difference in the two strategies' estimated profits. However, this approach can result in significant bias in the estimation of the value of VRA because of the assumption made on step (3), which is that the estimated yield response functions are the true yield response functions. @trevisan2021spatial provide an example. At step (3), they used their estimated GWR as the true yield response functions. This assumption is generally unavoidable for researchers since they cannot observe any real field's true yield response function of any real field. Use of these procedures assumes accurate estimation of yield response functions, which when untrue can result in significant bias in the estimation of the value of VRA. This bias problem can be particularly severe when the method used tends to exaggerate the true heterogeneity in yield response functions. We suspect that the high value of VRA estimated by @trevisan2021spatial displays this bias.

In the following, we pursue the two objectives just described above by conducting Monte Carlo simulations in which we first generate and then analyze stylized OFPE data. We cannot test which model specification results in more profitable site-specific nitrogen rate recommendations using real data because it is impossible to observe the true yield response functions. For the same reason, we cannot test whether @trevisan2021spatial over-estimates the actual value of VRA, either. But in the Monte Carlo simulations we specify yield response functions and generate stylized data from those functions, which enables us to quantify in the context of the simulations the value of GWR and the bias in GWR-based estimation of the value of VRA. Monte Carlo simulations are commonly used in this way to gain insights into the statistical properties of trial designs and estimations methods [@mckinion2001analysis; @gebbers2010application; @bullock2020value; @alesso2021design].

One of the principal findings of this article is that the model specification used by @trevisan2021spatial creates more valuable information than does the model specification used by @rakshit2020 under usual corn and N fertilizer prices. This is primarily due to GWR's poor local estimation of the coefficients on $N^2$. Since the coefficients on $N^2$ is highly influential in determining site-specific EONR, inaccuracy in its estimation can result in significant economic loss. We also show that even under the method used by @trevisan2021spatial, the benefit of VRA over URA is rather small, averaging only about \$5 ha$^{-1}$; we conclude that both @rakshit2020 and @trevisan2021spatial significantly over-estimated that value. Our results suggest that the prospects of using GWR to generate site-specific input recommendations are bleaker than stated in @trevisan2021spatial.

@@

To find the bias in estimating the value of VRA, the "estimated" profits of the SCAM-based URA and GWR-based VRA were calculated by plugging in the estimated optimal nitrogen rates into the cell-specific yield response functions estimated by GWR. Estimated per-ha net revenues for SCAM-based URA and GWR-based VRA are found as follows:

@@

Figure \@ref(fig:pi-dif-dist) shows the distribution of $\hat{\Delta}_{gwr-m}$, profit difference between the GWR-based VRA and the SCAM-based URA. The distribution of the value of VRA from GWR-R is centered around 0, indicating that VRA based on GWR-R is on average no more profitable than SCAM-based URA. This result comes from GWR-R's highly inaccurate estimation of the subplot-level $N$ and $N^2$ coefficients, which led to unreliable subplot-specific nitrogen rate recommendations. Figure \@ref(fig:true-vs-estimated-coef-gwr-r) illustrates the accuracy of GWR-R in estimating the $N$ and $N^2$ coefficients in one simulation round. Estimates of the $N^2$ coefficients are positive for some subplots, indicating an increasing marginal product of the nitrogen rate, which contradicts a well-established agronomic property. The result is consistent with the bottom panel of Figure 12 in @rakshit2020 as well as the widely criticized poor coefficient estimation accuracy of GWR model in the literature [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation]. Figure \@ref(fig:true-vs-estimated-optn-gwr-r) plots the estimated cell-specific optimal N against the true optimal N for the same simulation round, and again shows that GWR-R can be highly unreliable, and consequently that basing variable rate management on GWR-R may be no better than taking a simple URA approach. Basically, not enough information is available locally to estimate reliably the coefficients on both $N$ and $N^2$ by subplot.

The GWR-T approach, however, performed better than SCAM-URA in majority of cases, with some cases showing values-added exceeding \$10 ha$^{-1}$. This may seem surprising as the model estimated in the GWR-T approach is more restrictive than that in the GWR-R approach because the coefficient on $N^2$ is assumed to be global. However, unlike GWR-R, this restriction helps avoid estimating positive subplot-level coefficients on $N^2$. This result implies that the value of avoiding highly unreliable estimates of coefficients on $N^2$ subplot-specifically was greater than loss of local flexibility in the coefficients on $N^2$.

@@

Next we examine the bias in the "estimated" value of GWR-based VRA that researchers would encounter using real data. Figure \@ref(fig:bias-est-pi) shows the distribution of the bias in "estimated" profit between the GWR-based VRA and SCAM-based URA. Unlike the true difference in profit, VRA based on GWR-R appears to perform overwhelmingly better, with its average profit about \$`r round(pi_dif_gwr, digits = 2)` ha$^{-1}$ greater than that of the SCAM-based URA. That is, researchers would tend to significantly over-estimate the value of VRA based on GWR-R. When the GWR estimates are considered to define true yield response, the inaccuracy of GWR-R generates over-estimation of the heterogeneity of yield response within the field, which can lead to significant over-estimation of the value of GWR-R itself. Under GWR-T, the bias is more than \$10 ha$^{-1}$ for `r results[type == "GWR-T", mean(abs(bias) > 10)] * 100` % of the simulation cases: under GWR-R, that bias is greater than \$10 ha$^{-1}$ in `r results[type == "GWR-R", mean(abs(bias) > 10)] * 100` % of the simulated cases. However, as can be seen in the bottom panel of Figure \@ref(fig:bias-est-pi), the distribution of bias from GWR-T has a fatter tail than GWR-R with more mass on higher bias values. Bias is more than \$50 ha$^{-1}$ for `r results[type == "GWR-T", mean(abs(bias) > 50)] * 100` % of the simulation cases for GWR-T as opposed to `r results[type == "GWR-R", mean(abs(bias) > 50)] * 100` % for GWR-R.

Figure \@ref(fig:why-bias-many) illustrates how over-estimations can occur. It shows yield response functions estimated by GWR-T and estimated yields associated with the GWR-based EONR rates and SCAM-based EONR rates for 50 randomly chosen cells in a single simulation. Since GWR-based EONRs were obtained assuming the yield response functions estimated by GWR, by construction they out-perform better the SCAM-based estimates in every cell. For many cells, the SCAM-based estimated EONR is significantly higher than the actual yield-maximizing N rate, resulting in a yield far lower because of the quadratic functional form assumption. Figure \@ref(fig:why-bias-single) focuses on a single cell and compares estimated and true yields between GWR and SCAM (panel (a)) and estimated and true profits between GWR and SCAM (panel (b)). The cell's true yield response functions plateaus at a nitrogen rate of about $140$ kg ha$^{-1}$, but the GWR-estimated yield response function suggests that yield should peak at a nitrogen rate of about $190$ kg ha$^{-1}$ and then yield declines afterward. In reality, the yield differential between GWR and SCAM is 0, while the estimated yield differential is about $0.25$ ton ha$^{-1}$, leading to the over-estimation of the value of GWR in panel (b). Based on the true profit response curve, applying the GWR-based recommendation is about \$`r round(- true_yield_data[type != "True", diff(profit)], digits = 0)` ha$^{-1}$ more profitable than applying the SCAM-based recommendation. This profit differential comes soley from the difference in nitrogen cost since GWR and SCAM yields are equal. However, if calculations are based on the cell's GWR-based estimation of the response function, profits from the GWR-based recommendation are measured to be about \$`r round(- point_data_gwr[, diff(profit)], digits = 0)` ha$^{-1}$ greater than from the SCAM-based recommendation. Beyond the difference in nitrogen cost, the falsely estimated yield boost by GWR contributes to the profit differential, thus significantly over-estimating the actual value of GWR.

@@

Our simulation results show the basic GWR model (GWR-R) has little economic value for site-specific $R_xs$. The GWR-R based VRA is on average no more profitable than SCAM-based URA under historically common price scenarios. This finding reveals the economic consequences of the widely recognized statistical inaccuracy issue of GWR estimation [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation], and in agreement with the previous critique that GWR should be used as an exploratory tool rather than an inferential tool [@wheeler2005multicollinearity; @paez2011simulation]. Precision agriculture practitioners should be cautious when using GWR for site-specific $R_xs$. If GWR-based approach must be employed to find site-specific input recommendations (e.g., due to lack of field and soil information), our simulation results show that GWR-T performs relatively better than GWR-R, though its profitability improvement against URA is only moderate.

An obvious cause of the GWR models' poor economic performances in this work is the quadratic functional form used in GWR that differs from the true quadratic-plateau yield response functions. One solution could be to upgrade to nonlinear GWR models. @lambert2022geographically have recently developed a linear-plateau GWR model, which could be worthy of future examinations of its economic value. Another solution is to extend the parametric GWR approaches to a semi-parametric or non-parametric GWR where the yield response functions are estimated without assuming particular functional forms (like SCAM). However, such a method is likely to encounter a very similar problem to that faced by GWR-R: insufficient information available locally to estimate reliably the shape of yield response curve locally. It is also noted that the recently developed multiscale GWR model [@fotheringham2017multiscale; @yu2020inference; @comber2022route] allows the bandwidth to be derived separately for each covariate in the model, which would potentially improve the performances of GWR estimates and be incorporated into future research. Please note, however, that multiscale GWR models are not necessary in out simulations as we have only one covaraite ($N$) in our simulations.

It is important to be aware that researchers need to be extremely cautious about their estimated value of VRA based on GWR whether they follow GWR-R or GWR-T. Our results show that it is likely that they will over-estimate their true values and the bias can be misleadingly high at the non-negligible probability. Extremely high values of VRA reported in @trevisan2021spatial are likely to have reflected this bias. Indeed, the bias problem we raised here is likely to be observed for other statistical methods because the bias comes from the assumption that the _estimated_ yield response functions are true. Whatever the underlying statistical method for yield response functions may be, researchers are likely to overestimate the true value of their methods. It would be an interesting future research to investigate the bias in other major statistical methods that are commonly used in the literature.

@@

This article examined the economic value of GWR-based VRA and the bias in its estimation in the context of OFPE. We showed that restricting the coefficient on $N^2$ to a global parameter as done in @trevisan2021spatial leads to site-specific nitrogen rate recommendations with higher profits compared to the specification used by @rakshit2020, which allows the coefficients on $N^2$ to vary locally. However, we also found that both specifications can result in significant over-estimation of the true value of GWR-based site-specific nitrogen rate recommendations. It can be concluded that researchers need to be cautious about promoting the GWR-based approach in VRA recommendation.

@@

```{r, fig.id = "pi-dif-dist", fig.cap = "The value of GWR-based VRA over SCAM-based URA for GWR-R and GWR-T"}
g_value
```

```{r fig.id = "true-vs-estimated-coef-gwr-r", fig.cap = "Comparison of Estimated and True Coefficients"}
g_comp_coef
```

@@

```{r fig.id = "bias-est-pi", fig.cap = "Bias in the estimation of the value of GWR-based VRA over SCAM-based URA for GWR-R and GWR-T"}
g_bias
```

>>>>

```{r figure_setup, cache = F}
theme_update(
  axis.title.x =
    element_text(
      size = 12, angle = 0, hjust = .5, vjust = -0.3, family = "Times"
    ),
  axis.title.y =
    element_text(
      size = 12, angle = 90, hjust = .5, vjust = .9, family = "Times"
    ),
  axis.text.x =
    element_text(
      size = 10, angle = 0, hjust = .5, vjust = 1.5, family = "Times"
    ),
  axis.text.y =
    element_text(
      size = 10, angle = 0, hjust = 1, vjust = 0, family = "Times"
    ),
  axis.ticks =
    element_line(
      size = 0.3, linetype = "solid"
    ),
  axis.ticks.length = unit(.15, "cm"),
  #--- legend ---#
  legend.text =
    element_text(
      size = 10, angle = 0, hjust = 0, vjust = 0, family = "Times"
    ),
  legend.title =
    element_text(
      size = 10, angle = 0, hjust = 0, vjust = 0, family = "Times"
    ),
  legend.key.size = unit(0.5, "cm"),
  #--- strip (for faceting) ---#
  strip.text = element_text(size = 10),
  #--- plot title ---#
  plot.title = element_text(family = "Times", face = "bold", size = 12),
  #--- margin ---#
  # plot.margin = margin(0, 0, 0, 0, "cm"),
  #--- panel ---#
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background = element_blank(),
  panel.border = element_rect(fill = NA)
)
```

@@

**Abstract**: Geographically weighted regression (GWR) has been presented as a prominent tool to estimate site-specific yield response functions to generate site-specific input rate recommendations using data generated by on-farm precision experimentation (OFPE). The key objectives of this paper are two-fold. First, it evaluates economically the two sets of functional-form specifications used by two recent published studies of site-specific input management that apply GWR to data from OFPE. We show that the relative performance of the two approaches vary depending on the crop-fertilizer price ratios due to their tendency to over-/under-estimate EONR. Second and more important, we investigate the possibility of bias in estimating the economic value of site-specific recommendation maps based on GWR. We show that both GWR approaches suffer significant positive bias, which can lead to large over-estimation of the economic value of applying GWR methods. Our study is the first to systematically examine the economic (not statistical) properties of the use of GWR in OPFE settings. We reveal that in many circumstances using GWR is far less profitable than claimed by previous studies, which provides a necessary cautionary message to researchers who might otherwise “over-sell” to other researchers the value of using GWR methods in empirical work involving the estimation of site-specific input management.

@@

In recent years, On-farm Precision Experimentation (OFPE) has gained traction with both researchers and practitioners as a means of generating high-resolution spatial data to inform site-specific crop input management decisions [@bullock2019data; @lacoste2021farm]. Accompanying interest is surging among researchers in identifying efficient statistical methods to estimate site-specific yield response functions, which have examined various methods, ranging from Geographically Weighted Regression (GWR) [@rakshit2020; @evans2020assessment; @trevisan2021spatial] to machine learning methods including random forest [@krause2020random], convolutional neural network [@barbosa2020modeling], and causal forest [@kakimoto2022causal] approaches. Among these methods applied to OFPE data, GWR is distinct in that it does not require potentially costly collection of site-specific field and soil information in estimating site-specific yield response functions.

@@

However, deploying sophisticated sensors to gather field characteristics data is also costly, and the effects of their generation and use on farming profitability remains in question [@gardner2021economic]. Recognizing the significant costs of obtaining useful, high-resolution soil and field properties data, @trevisan2021spatial demonstrated a method of providing site specific management recommendations without such data. The study estimated site-specific yield response functions by applying GWR techniques on data from OFPEs [@bullock2019data]. @trevisan2021spatial reported dramatic results, estimating an average potential gain of \$65 ha$^{-1}$ from applying seed and N at optimal uniform rates (instead of at the rates the farmers would have chosen if not participating in the research), and an additional potential gain of \$58 ha$^{-1}$ when changing from optimal uniform application rates to optimal site-specific application rates. This is rather surprising give the poor statistical accuracy of GWR estimates [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation]. @rakshit2020 also applied GWR to on-farm experiment data. However, while they did estimate site-specific yield response functions, they did not derive site-specific economically optimal nitrogen rates based on them, and thus did not conduct economic analysis unlike @trevisan2021spatial. @evans2020assessment explored using GWR with a linear model specification to detect low- and high-response areas, but like @rakshit2020, they also did not estimate site-specific economically optimal nitrogen rates.

@@

Second, we will examine the degree and direction of bias in the estimation of the economic value of GWR-based variable rate application (VRA) and question the extremely high estimates of that value reported by @trevisan2021spatial. It is critical to keep in mind that it is not our objective at all to see the bias in the coefficient estimation by GWR, unlike [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation]. Rather, we are interested in the economic implication of the statistical inaccuracy in estimating the coefficients of the model in this study. In general, researchers take the following steps to estimate the value of VRA using OFPE data [e.g., @anselin2004spatial; @swinton1998evaluating; @bullock2002adding; @liu2006site]: (1) estimate site-specific yield response functions based on a method chosen by the researcher; (2) use the estimated yield response functions to estimate the economically optimal site-specific input rates (EOIR) and economically optimal uniform input rates; (3) plug the estimated site-specific EOIRs and uniform EOIR into the estimated yield response functions to calculate estimated profits under both strategies; and (4) find the difference in the two strategies' estimated profits. However, this approach can result in significant bias in the estimation of the value of VRA because of the assumption made on step (3), which is that the estimated yield response functions are the true yield response functions. @trevisan2021spatial provide an example. At step (3), they used their estimated GWR as the true yield response functions. This assumption is generally unavoidable for researchers since they cannot observe any real field's true yield response function of any real field. Use of these procedures assumes accurate estimation of yield response functions, which when untrue can result in significant bias in the estimation of the value of VRA. This bias problem can be particularly severe when the method used tends to exaggerate the true heterogeneity in yield response functions. We suspect that the high value of VRA estimated by @trevisan2021spatial displays this bias.

In the following, we pursue the two objectives by conducting Monte Carlo simulations in which we first generate and then analyze stylized OFPE data. We cannot test which model specification results in more profitable site-specific nitrogen rate recommendations using real data because it is impossible to observe the true yield response functions using real-world data. For the same reason, we cannot test whether @trevisan2021spatial over-estimates the actual value of VRA, either. But in the Monte Carlo simulations we specify yield response functions and generate stylized data from those functions, which enables us to quantify in the context of the simulations the value of GWR and the bias in GWR-based estimation of the value of VRA. Monte Carlo simulations are commonly used in this way to gain insights into the statistical and economic properties of trial designs and estimations methods [@mckinion2001analysis; @gebbers2010application; @bullock2020value; @alesso2021design].

One of the principal findings of this article is that the model specification used by @trevisan2021spatial tends to outperforms that by @rakshit2020 when the ratio of nitrogen price to corn price is low (nitrogen is relatively cheap), but the relationship reverses when the price ratio is high. This is due the tendency of the specification by @trevisan2021spatial and @rakshit2020 to over- and under-estimate EONR, respectively. We also show that the benefit of VRA over URA is rather small irrespective of which specification to use, averaging only about \$5 ha$^{-1}$; we conclude that both @rakshit2020 and @trevisan2021spatial would significantly over-estimate that value. Our results suggest that the prospects of using GWR to generate site-specific input recommendations are bleaker than stated in @trevisan2021spatial.

<span style = "color: blue;"> this needs to be rewritten </span>

@@

To find the bias in estimating the value of VRA, the l rofitsof the SCAM-based URA and GWR-based VRA were calculated by plugging in the estimated optimal nitrogen rates into the cell-specific yield response functions estimated by GWR. Estimated per-ha net revenues for SCAM-based URA and GWR-based VRA are found as follows:

@@

Figure \@ref(fig:pi-dif-dist) shows the distribution of $\Delta_{gwr-m}$, true profit difference between the GWR-based VRA and the SCAM-based URA, at various price scenarios. The comparative advantage of GWR-R and GWR-T varies significantly depending on nitrogen-corn price ratio. Specifically, GWR-R performs better as the price ratio increases (as nitrogen becomes more expensive relative to corn), while the opposite is the case for GWR-T. At the low price ratio of 4.16 and 5.44, VRA based on GWR-R is no better than SCAM-based URA. However, when the price ratio is $10.35$, the median benefit of GWR-R is `r round(mean_data_value[type == "GWR-R" & pLabel == "10.35", pi_diff], digits = 2)`. On the other hand, the median benefit of VRA based on GWR-T when the price ratio is 4.16 is `r round(mean_data_value[type == "GWR-T" & pLabel == "4.16", pi_diff], digits = 2)`, but the its benefit is even negative at `r round(mean_data_value[type == "GWR-T" & pLabel == "10.35", pi_diff], digits = 2)` when the price ratio is 10.35.

Figure \@ref(fig:bias-est-eonr) provides insights into this phenomenon, which shows the distribution of average ratio of estimated EONR to true EONR. A value lower than 1 means EONR is underestimated on average. GWR-R tends to over-estimate EONR at lower price ratios, but the magnitude of over-estimation goes down as the price reatio goes up. The opposite trend is true for GWR-T. At the price ratio of 10.35, the degree of EONR over-estimation is quite significant. Since high-price ratio means nitrogen is relatively expensive, over-estimation of EONR hurts more economically compared to the cases with lower price ratios.

Figure \@ref(fig:true-vs-estimated-optn-gwr-r) presents the estimated site-specific EONR plotted against true site-specific EONR by GWR approach for a single simulation round. Even though it is just for a single simulation round, it is illustrative in understanding the difference in GWR-R and GWR-T. Neither Site-specific EONR estimated by GWR-R is not very accurate, but inaccurate in a different manner. The range of EONR estimates by GWR-R is very wide due to the fact that the coefficient on $N^2$ is allowed to vary site specifically in GWR-R. Since the estimation of the coefficient on $N^2$ is highly inaccurate, the range of estimated EONR is much wider than the range of true site-specific EONR. On the contrary, GWR-T has a very narrow range of EONR estimates. This is due to the fact that the coefficient on $N^2$ is constrained to be the same for all the sites. Consequently, GWR-T fails to capture the true heterogeneity in EONR. Therefore, they fail to estimate site-specific EONR well for different reasons.

@@

Next, we examine the bias in the estimated value of GWR-based VRA. Figure \@ref(fig:bias-est-pi) shows the distribution of the bias in the estimation of the value of GWR-based VRA over SCAM-based URA (profit difference between the GWR-based VRA and SCAM-based URA). For example, the value of 10 would mean that the estimated value of GWR-based VRA over-estimates its true value by $10 per ha. As the figure suggests, VRA based on GWR-R appears to perform overwhelmingly better than it truly is, presenting significant positive bias across the price range. That is, researchers would tend to significantly over-estimate the value of VRA based on GWR-R. When the GWR estimates are considered to define true yield response, the inaccuracy of GWR-R generates over-estimation of the heterogeneity of yield response within the field, which can lead to significant over-estimation of the value of GWR-R itself.

GWR-T exhibits a different pattern of bias. At low price ratios, GWR-T approach has smaller bias compared to GWR-R. This is partially because GWR-T tends to understate the heterogeneity of site-specific yield response function as we saw in figure \@ref(true-vs-estimated-optn-gwr-r). As the price ratio goes up, bias becomes greater. This is due to significant over-estimation of EONR by GWR-T as we saw in figure \@ref(fig:bias-est-eonr). Unlike the GWR-R approach, the distribution of the bias by the GWR-T approach has a fat tail, indicating that there is a greater chance of encountering large positive bias in the value of VRA over URA.

Figure \@ref(fig:why-bias-many) illustrates how over-estimation of the value of VRA can occur. It shows yield response functions estimated by GWR-T and estimated yields associated with the GWR-based EONR rates and SCAM-based EONR rates for 50 randomly chosen cells in a single simulation. Since GWR-based EONRs were obtained assuming the yield response functions estimated by GWR, they out-perform the SCAM-based estimates in every cell by construction. For many cells, the SCAM-based estimated EONR is significantly higher than the actual yield-maximizing N rate, resulting in a yield far lower because of the quadratic functional form assumption. Figure \@ref(fig:why-bias-single) focuses on a single cell and compares estimated and true yields between GWR and SCAM (panel (a)) and estimated and true profits between GWR and SCAM (panel (b)). The cell's true yield response functions plateaus at a nitrogen rate of about $140$ kg ha$^{-1}$, but the GWR-estimated yield response function suggests that yield should peak at a nitrogen rate of about $190$ kg ha$^{-1}$ and then yield declines afterward. In reality, the yield differential between GWR and SCAM is 0, while the estimated yield differential is about $0.25$ ton ha$^{-1}$, leading to the over-estimation of the value of GWR in panel (b). Based on the true profit response curve, applying the GWR-based recommendation is about \$`r round(- true_yield_data[type != "True", diff(profit)], digits = 0)` ha$^{-1}$ more profitable than applying the SCAM-based recommendation. This profit differential comes solely from the difference in nitrogen cost since GWR and SCAM yields are equal. However, if calculations are based on the cell's GWR-based estimation of the response function, profits from the GWR-based recommendation are measured to be about \$`r round(- point_data_gwr[, diff(profit)], digits = 0)` ha$^{-1}$ greater than from the SCAM-based recommendation. Beyond the difference in nitrogen cost, the falsely estimated yield boost by GWR contributes to the profit differential, thus significantly over-estimating the actual value of GWR.

@@

Our simulation results show the basic GWR model (GWR-R) tends to have little economic value for site-specific $R_xs$. The GWR-R based VRA is on average no more profitable than SCAM-based URA under many price scenarios particularly when nitrogen price is relatively low compared to corn price. This finding reveals the economic consequences of the widely recognized statistical inaccuracy issue of GWR estimation [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation], and in agreement with the previous critique that GWR should be used as an exploratory tool rather than an inferential tool [@wheeler2005multicollinearity; @paez2011simulation]. Precision agriculture practitioners should be cautious when using GWR for site-specific $R_xs$. If GWR-based approach must be employed to find site-specific input recommendations (e.g., due to lack of field and soil information), our simulation results show that GWR-T performs relatively better than GWR-R, though its profitability improvement against URA is only moderate.

An obvious cause of the GWR models' poor economic performances in this work is the quadratic functional form used in GWR that differs from the true quadratic-plateau yield response functions. One solution could be to upgrade to nonlinear GWR models. @lambert2022geographically have recently developed a linear-plateau GWR model, which could be worthy of future examinations of its economic value. Another solution is to extend the parametric GWR approaches to a semi-parametric or non-parametric GWR where the yield response functions are estimated without assuming particular functional forms (like SCAM). However, such a method may well encounter a very similar problem to that faced by GWR-R: insufficient information available locally to estimate reliably the shape of yield response curve locally. It is also noted that the recently developed multi-scale GWR model [@fotheringham2017multiscale; @yu2020inference; @comber2022route] allows the bandwidth to be derived separately for each covariate in the model, which would potentially improve the performances of GWR estimates and be incorporated into future research. Please note, however, that multi-scale GWR models are not necessary in our simulations as we have only one covariate ($N$) in our simulations.

Most important, it is crucial to be aware that researchers need to be extremely cautious about their estimated value of VRA based on GWR whether they follow GWR-R or GWR-T. Our results show that it is likely that they will over-estimate their true values and the bias can be misleadingly high at the non-negligible probability. Extremely high values of VRA reported in @trevisan2021spatial are likely to have reflected this bias. Indeed, the bias problem we raised here is likely to be observed for other statistical methods because the bias comes from the assumption that the _estimated_ yield response functions are true. Whatever the underlying statistical method for yield response functions may be, researchers are likely to overestimate the true value of their methods. It would be an interesting future research to investigate the bias in other major statistical methods that are commonly used in the literature.

@@

This article examined the economic value of GWR-based VRA and the bias in its estimation in the context of OFPE. We showed that VRA based on GWR provides small economic benefits over URA based on SCAM. The relative performance of the model specifications used by @trevisan2021spatial and @rakshit2020 differs based on nitrogen-corn price ratio. Finally and most important, we found that both specifications can result in significant over-estimation of the true value of GWR-based site-specific nitrogen rate recommendations. It can be concluded that researchers need to be cautious about promoting the GWR-based approach in VRA recommendation.

@@

```{r, fig.id = "pi-dif-dist", fig.cap = "The value of GWR-based VRA over SCAM-based URA for GWR-R and GWR-T", fig.height = 5, fig.width = 6}
g_value
```

```{r fig.id = "true-vs-estimated-coef-gwr-r", fig.cap = "Comparison of Estimated and True Coefficients", eval = F}
g_comp_coef
```

@@

```{r fig.id = "bias-est-eonr", fig.cap = "Average bias in the estimation of EONR by GWR-R and GWR-T", fig.height = 5, fig.width = 6}
g_eonr_bias
```

```{r fig.id = "bias-est-pi", fig.cap = "Bias in the estimation of the value of GWR-based VRA over SCAM-based URA for GWR-R and GWR-T", fig.height = 5, fig.width = 6}
g_bias
```
